Compositional Certified Resource Bounds

### 2014-07-02 paper/main.tex
conclusion

@@

cite flops

>>>>

There are techniques~\cite{Braberman08} that can compute the memory
requirements of object oriented programs with region based garbage
collection.  These systems infer invariants and use external tools
that count the number of integer points in the corresponding polytopes
to obtain bonds.  The described technique can handle loops but not
recursive or composed functions.

@@

We have introduced an novel quantitative analysis system for CompCert
Clight programs.  To the best of our knowledge, this article presents
the first resource analysis framework for C that makes it possible to
combine non-trivial automatically derived bounds with interactively
derived bounds in a proof system that produces verifiable certificates
for the bounds.  The main technical innovations are a quantitative
Hoare logic for reasoning about user-defined resource cost and an
automatic amortized analysis that derives bounds for programs whose
resource consumption depends on (possibly negative) integers and
non-sequential control flow as introduced by \code{break} and
\code{return} statements.

We will continue to improve our framework with the goal of reasoning
about resource usage of system software such as the hypervisor kernel
CertiKOS~\cite{GuVFSC11}, which we are currently developing and
verifying.  For on thing, we will improve the automation to derive
\emph{polynomial bounds} and to handle non-linear size changes, as
already developed for functional programs~\cite{HoffmannS13}.  For
another thing, we will build on previous work~\cite{HoffmannMZ13}
the generalize the quantitative Hoare logic to handle \emph{concurrent
  programs} with locks and lock-free data structures.
